--- 
title       : Link Prediction
subtitle    : Social Network Analysis HW2
author      : 'R03922142 Yu Ran , R03922145 Yi Huang , R03944049 Bowen Yuan'
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme: zenburn      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
    user: hyiiego
    repo: present_demo
--- 

<!-- Limit image width and height -->
<style type='text/css'>
img {
    max-height: 560px;
    max-width: 964px;
}
</style>

<!-- Center image on slide -->
<script src="http://ajax.aspnetcdn.com/ajax/jQuery/jquery-1.7.min.js"></script>
<script type='text/javascript'>
$(function() {
    $("p:has(img)").addClass('centered');
});
</script>


## All the way down

&nbsp;

&nbsp;


### - Explore the graph

### - Select candidate

### - Probe baseline method

### - Experiment learning method 

### - Compare method



--- &twocol w1:40% w2:40%


## Distributions

&nbsp;

*** =left

```{r,echo=FALSE,fig.height=5,fig.width=6.5}
library(data.table)
library(RJSONIO)
library(ggplot2)
library(reshape2)
library(scales)

degree <- fread('/Users/Hyiiego/Documents/Dropbox/NTU/SNA/hw2/result.csv')
ggplot(data=degree,aes(x=value,y=count)) + geom_point() + 
    ggtitle('#friends distribution of all nodes') + 
    labs(x = '#friends') +
  theme(axis.title.x = element_text(size = 16, colour = 'black'),
         axis.title.y = element_text(size = 16, colour = 'black', angle = 90),title = element_text(size = 16, colour = 'black'),
        axis.text=element_text(size=16))
```

*** =right

```{r,echo=FALSE,fig.height=5,fig.width=6.5,warning=FALSE}
degree <- fread('/Users/Hyiiego/Documents/Dropbox/NTU/SNA/hw2/result.csv')
ggplot(data=degree,aes(x=value,y=test_count)) + geom_point() + 
    ggtitle('#friends distribution of test nodes') + 
    labs(x = '#friends') +
  theme(axis.title.x = element_text(size = 14, colour = 'black'),
         axis.title.y = element_text(size = 14, colour = 'black', angle = 90),title = element_text(size = 14, colour = 'black'),
        axis.text=element_text(size=14))
```

--- 

## Candidate Selection

from all nodes in graph to people who is within 3-step distance from the target node

&nbsp;

```{r,echo=FALSE,fig.height=3.5,fig.width=10}
second <- fread('/Users/Hyiiego/Documents/Dropbox/NTU/SNA/hw2/report/second_length.csv')
second$v = 'length'
second$V1 = as.factor(second$V1)
ggplot(second,aes(x = v, y = V2,fill = V1)) + 
    geom_bar(position = "fill",stat='identity') + 
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    ggtitle('the second shortest path length between two nodes \n') + 
    labs(x = ' ',y = 'total number of pair') +
    theme(axis.title.x = element_text(size = 16, colour = 'black'),
          axis.title.y = element_text(size = 16, colour = 'black', angle = 90),
          title = element_text(size = 16, colour = 'black'),          
          axis.text=element_text(size=16),
          legend.position='bottom',
          legend.title=element_blank(),
          legend.text=element_text(size=16)) +
          guides(fill = guide_legend(keywidth = 1.4, keyheight = 1.4)) 
```

---

## Preliminary Probes

### Methods Based on Node Neighborhoods
  - Common Neighbors(F1-score:0.103298 MAP:0.083843)
  
  - Jaccard's coefficient
  - Adamic/Adar $\bigstar$ (F1-score:0.112816 MAP:0.083212)
  
  - Resource Allocation Index
  
  
### Methods Based on All Paths
  - Preferential Attachment
  
### With Community Information


---


## Number of recommmendation

&nbsp;

### - Based on threshold

### - Corresponding to degree
    - Common Neighbors: 50%
    - Adamic/Adar: 30%

---

## Learning Method

### Collaborative Filtering

using adjacency matrix as feature

### Classification(one-class & two-class)

- Data Sampling - select training set and validate set

- Feature extraction - combine user profile and topological features

- Models - logistic regression, SVM

---


## Tools and Packages

&nbsp;

### - Graphlab

### - NetworkX

### - Scikit-learn

### - MongoDB

---


## Conclusion

&nbsp;

### - from bottom to top

### - deal with unbalancing

### - time is everything


--- 

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

## Thank You!


